Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-26 NEUROC/sec3-experiment-design.tex
更新了sec3和4

    \item[Q4] \emph{Could sampling techniques remove performance bottlenecks in GNN training? What was the performance bottleneck of sample-based inference? Did the use of sampling techniques in training affect model accuracy? } (Section~\ref{sec:effects_of_sampling_techniques_on_performance})

          Theoretically, sampling techniques could significantly reduce the number of graph neurons that participated in the training of a batch.
          %
          Consequently, the processing time and memory usage per batch should also decrease.
          %
          The model accuracy of GNNs might also be affected.
          %
          To validate the effectiveness of sampling techniques, we measured the training time, peak memory usage, and test accuracy under different batch sizes.
          %
          If sampling techniques are effective, they would be the keys to conduct GNN training on very big graphs.
          %
          If they were not effective, we wanted to find out which impaired their efficiency.
          %
          % TODO: 补充Sample-based Inference的介绍

>>>>

    \item[Q4] \emph{Could sampling techniques remove performance bottlenecks in GNN training/inference? Did the use of sampling techniques in training affect model accuracy? } (Section~\ref{sec:effects_of_sampling_techniques_on_performance})

          Theoretically, sampling techniques could significantly reduce the number of graph neurons that participated in the training of a batch.
          %
          Consequently, the processing time and memory usage per batch should also decrease.
          %
          The model accuracy of GNNs might also be affected.
          %
          To validate the effectiveness of sampling techniques, we measured the training/inference time, peak memory usage, and test accuracy under different batch sizes.
          %
          If sampling techniques are effective, they would be the keys to conduct GNN training/inference on very big graphs.
          %
          If they were not effective, we wanted to find out which impaired their efficiency.
          %

### 2020-12-26 NEUROC/sec4-experiments.tex
更新了sec3和4

\paragraph{Memory Usage of Inference}

Figure~\ref{fig:exp_inference_memory_expansion_ratio} shows the memory expansion ratios of typical GNNs during inference.
%
Since no intermediate results had to be cached during inference of GGNN, GAT, and GaAN,
the memory expansion ratios of inference were much less than training for the three GNNs (\figurename~\ref{fig:exp_memory_expansion_ratio}).
%
The MERs of inference were 45\% to 83\% (GGNN), 52\% to 61\% (GAT), and 37\% to 69\% (GaAN) of training.
%
However, the MERs were still high, disallowing inferencing with big graphs.
%
To handle big graphs, the sample-based inference was necessary.

\begin{figure}[H]
   \centering
   \subfloat{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}}
   \caption{Memory expansion ratios of typical GNNs in Inference.}
   \label{fig:exp_inference_memory_expansion_ratio}
\end{figure}

\paragraph{Summary}
%TODO: 
The \emph{high} memory expansion ratio severely restricted the data scalability of GNN training and inference.
%
The memory usage mainly came from the intermediate results of the \emph{edge calculation stage}.
%
Fixing the number of vertices, the memory usage increased \emph{linearly} along with the number of edges.
%
Fixing the GNN structure and the hyper-parameters, increasing the dimension of input feature vectors could reduce the memory expansion ratio.
%
To reduce the memory usage of GNN training, optimizations should focus on reducing memory footprints of the edge calculation stage.

@@

\paragraph{Summary of Sampling Techniques}
% TODO:
The sampled subgraphs had lower average degrees than the original graph.
%
With small batch sizes, the sampling techniques could significantly reduce the training time per batch and the peak memory usage.
%
However, small batch sizes could not make full use of the computing power of a GPU.
%
With big batch sizes, the current implementation of the sampling techniques in PyG was inefficient.
%
The time spent on the sampling phase and the data transferring phase even exceeded the training phase.

>>>>

\paragraph{Comparing Inference and Training}

Figure~\ref{fig:memory_usage_analysis} shows the memory expansion ratios of typical GNNs during inference.
%
Since no intermediate results had to be cached during inference of GGNN, GAT, and GaAN,
the memory expansion ratios of inference were much less than training for the three GNNs (\figurename~\ref{fig:exp_memory_expansion_ratio}).
%
The MERs of inference were 45\% to 83\% (GGNN), 52\% to 61\% (GAT), and 37\% to 69\% (GaAN) of training.
%
However, the MERs were still high, disallowing inferencing with big graphs.
%
To handle big graphs, the sample-based inference was necessary.

\begin{figure}[H]
   \centering
   \subfloat{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}}
   \caption{Memory expansion ratios of typical GNNs in Inference.}
   \label{fig:memory_usage_analysis}
\end{figure}

%
We also did experiments about the effects of input feature dimension, average degrees, and the number of vertices on GNN inference memory usage.
%
The results were similar to the GNN training phase.
%

\paragraph{Summary of Memory Usage Analysis}
%
The \emph{high} memory expansion ratio severely restricted the data scalability of GNN training and inference.
%
The memory usage mainly came from the intermediate results of the \emph{edge calculation stage}.
%
Fixing the number of vertices, the memory usage increased \emph{linearly} along with the number of edges.
%
Fixing the GNN structure and the hyper-parameters, increasing the dimension of input feature vectors could reduce the memory expansion ratio.
%
To reduce the memory usage of GNN training and inference, optimizations should focus on reducing memory footprints of the edge calculation stage.

@@

\paragraph{Summary of Sampling Techniques}
% 
The sampled subgraphs had lower average degrees than the original graph.
%
With small batch sizes, the sampling techniques could significantly reduce the training/inference time per batch and the peak memory usage.
%
However, small batch sizes could not make full use of the computing power of a GPU.
%
With big batch sizes, the current implementation of the sampling techniques in PyG was inefficient.
%
The time spent on the sampling phase and the data transferring phase even exceeded the training/inference phase.
